Surrogate Modelling of the Tritium Breeding Ratio

### 2020-06-22 talk_ucl_cdt_200622/introduction.tex
update table and typesetting in the data generation slide

\begin{frame}
	\frametitle{Data Generation}
	We produced training and test datasets by uniform random sampling over the 7 discrete and 11 continuous parameters of Paramak.\newline
	 \begin{columns}[onlytextwidth,T]
      \column{\dimexpr\linewidth-7cm-5mm}

@@

        	\vspace{10pt}

        Two classes of runs:
        \begin{itemize}
            \item All parameters free.
            \item Discrete fixed, continuous free.
        \end{itemize}

      \column{7cm}
      \vspace{-0.5cm}
      \includegraphics[trim={0 0 0 2mm},clip,width=7cm]{params}

@@

		\begin{itemize}
			\item
				Regression performance: mean absolute error, $\sigma$ of
				error, $R^2$, $R^2_\text{adj.}$
			\item
				Computational complexity:
				training \& prediction time / sample.
		\end{itemize}

>>>>

\begin{frame}
	\frametitle{Data Generation}
	We produced training and test datasets by uniform random sampling over the 7
	discrete and 11 continuous parameters of Paramak.

	\begin{columns}[T]
		\column{0.34\textwidth}

		\vspace{5pt}

@@

		\vspace{5pt}

		2~classes of runs:
		\begin{itemize}
		\item All parameters free.
		\item Discrete fixed, continuous free.
		\end{itemize}

		\vspace{5pt}

		{\footnotesize
		Groups of fractions marked\textsuperscript{\textdagger\textdaggerdbl} are required to sum to 1.
		}

		\column{0.62\textwidth}
		\vspace{5pt}

		{\fontsize{8pt}{8pt}\selectfont
		\setlength\tabcolsep{3pt}
		\begin{tabular}{l|ll}
		\toprule
		{} & Parameter name & Domain\\
		\midrule
		\parbox[t]{2mm}{\hspace{-2pt}\multirow{12}{*}{\rotatebox[origin=c]{90}{Blanket}}}
		   & Breeder fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Breeder \isotope[6]{Li} enrichment fraction & $[0,1]$\\
		   & Breeder material & $\{\text{Li}_2\text{TiO}_3, \text{Li}_4\text{SiO}_4\}$\\
		   & Breeder packing fraction & $[0,1]$\\
		   & Coolant fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
		   & Multiplier fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Multiplier material & $\{\text{Be}, \text{Be}_{12}\text{Ti}\}$\\
		   & Multiplier packing fraction & $[0,1]$\\
		   & Structural fraction\textsuperscript{\textdagger} & $[0,1]$\\
		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
		   & Thickness & $[0,500]$\\
		\midrule
		\parbox[t]{2mm}{\hspace{-2pt}\multirow{6}{*}{\rotatebox[origin=c]{90}{First wall}}}
		   & Armour fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
		   & Coolant fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
		   & Coolant material & $\{\text{D}_2\text{O}, \text{H}_2\text{O}, \text{He}\}$\\
		   & Structural fraction\textsuperscript{\textdaggerdbl} & $[0,1]$\\
		   & Structural material & $\{\text{SiC}, \text{eurofer}\}$\\
		   & Thickness & $[0,20]$\\
		\bottomrule
		\end{tabular}
		}

@@

		\begin{itemize}
			\item
				Regression performance: mean absolute error, $\sigma$ of
				error, $R^2$, $R^2_\text{adj.}$
			\item
				Computational complexity:
				training \& prediction time / sample
		\end{itemize}
